\documentclass[../../../rasd.tex]{subfiles}
\begin{document}

\subsection{Requirements\label{sect:3.2.5}}
\begin{itemize}
	
	% TODO: Definition presenti in corsivo
	% TODO: numerare Req, 12a e 12b, aggiungere ultimi Req
	
	\item[R\subs{1}]At sign up, \ic{User} must provide: First name, last name, email and password;
	\item[R\subs{2}]At sign up, \ic{User} must accept \ic{Terms and conditions}, including the \ic{Privacy statement};
	\item[R\subs{3}]Identify a \ic{User} by his/her \ic{User identifier};
	\item[R\subs{4}]Receive \ic{User picture};
	\item[R\subs{5}]Receive \ic{User} choice for the type of \ic{Traffic violation};
	\item[R\subs{6}]Receive \ic{User position};
	\item[R\subs{7}]Send \ic{User picture} to the \ic{License plate recognition service};
	\item[R\subs{8}]Receive \ic{Ricognized license plate} from the \ic{License plate recognition service}.
	\item[R\subs{9}]Create \ic{User report} (? attaching Timestamp and User identifier to User picture, Recognized license plate and type of Traffic violation).
	\item[R\subs{10}]Store User report in SafeStreets Database.
	\item[R\subs{11}]Send User report to Municipality.
	\item[R\subs{}]Allow Users to request all their User report and the related Ticket feedback stored in SafeStreets Database at any time.
	\item[R\subs{}]Send to a specific User his/her User report stored.
	\item[R\subs{}]Query SafeStreets Database for a User by his/her identifer.
	\item[R\subs{}]Retrieve specific User reports by querying SafeStreets Database.
	\item[R\subs{}]Not send User report to Municipality if Chain of custody is broken.
	\item[R\subs{}]Receive Municipality data access request.
	\item[R\subs{}]Validate Municipality data access request.
	\item[R\subs{}]Allow Municipality to set specific constraints to define Detailed statistics.
	\item[R\subs{}]Send Detailed statistics to the requesting Municipality.
	\item[R\subs{}]Receive User report access request from User.
	\item[R\subs{}]Validate User report access request from User.
	\item[R\subs{}]Allow User to set specific constraints to define a group of User reports.
	\item[R\subs{}]Properly anonimyze the group of User reports defined by the User, in order to generate Public statistics.
	\item[R\subs{}]Send Public statistics to the requesting User.
	\item[R\subs{}]Send Accidents Database access request to Municipality. 
	\item[R\subs{}]Receive Accidents Database access confirmation from Municipality.
	\item[R\subs{}]Request Accidents data to Municipality.
	\item[R\subs{}]Receive Accidents data from Municipality.
	\item[R\subs{}]Generate Possible interventions crossing Municipality Accidents data with SafeStreets Database data.
	\item[R\subs{}]Send generated Possible interventions to Municipality.
	\item[R\subs{}]At sign up, Municipality must provide a Reference code.
	\item[R\subs{}]Identify Municipality by its Reference code.
	\item[R\subs{}]Receive Ticket feedback from Municipality.
	\item[R\subs{}]Store Ticket feedback in SafeStreets Database.
	\item[R\subs{}]... (Third party)
\end{itemize}

\end{document}